---
title: "vignette"
author: "Isaiah Valencia"
date: "6/11/2020"
output:
  pdf_document: default
  html_document: default
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(blblm)
library(tidyverse)
library(ISLR)
```

### Blblm in Action

*The following exemplifies blblm with and without parallelization. We are going to looking at Major League Baseball Data from the 1986 and 1987 seasons, from ISLR.*


first some traning and test data.
```{r,echo=FALSE}
data("Hitters")
Hitters <- na.omit(Hitters)
Hitters <- Hitters%>% dplyr::select(AtBat:Years, Salary)
size = round(.80*nrow(Hitters))
train_indices = sample( seq_len(nrow(Hitters)), size = size)

train = Hitters[train_indices,]
test = Hitters[-train_indices,]
```

Now lets fit a poisson, negative binomial, and a linear regression model using parallelization with 4 cores to compute. We are predicting Years in leagure for poisson and negative binomial regression, and hits for linear regression.
```{r}

poiss <- blblm(Years~ AtBat + Hits + HmRun + Runs + RBI + Walks + Salary , 
               data = train, model = 'poisson', m = 3, B = 100, para = TRUE, core = 4)

neg <- blblm(Years~ AtBat + Hits + HmRun + Runs + RBI + Walks + Salary, 
             data = train, model = 'neg', m = 3, B = 100, para = TRUE, core = 4)

linear <- blblm(Hits~AtBat + + HmRun + Runs + RBI + Walks + Years + Salary, 
                data = train, m = 3, B = 100, para = TRUE, core = 4)

models = list("poisson" = poiss,"negative binomial" = neg,"linear regression" = linear)

```

Here are the coefficient estimates for the models, using function `coef.blblm` with parallel computing using 4 cores.
```{r}
models %>% map( ~coef.blblm(.,para = TRUE, core = 4))
```

Confidence intervals can be computed for the estimates above using `confint.blblm` by parallel computing with 4 cores
```{r}
models %>% map( ~confint.blblm(.))
```

Another feature of blblm is preediction using parallel computing, with 4 cores. the first 5 predictions are shown.
```{r}
pred <- models %>% map( ~predict.blblm(.,test,para = TRUE,core = 4))
pred$poisson %>% map_dbl(~exp(.))[1:5]
pred$`negative binomial` %>% map_dbl(~exp(.))[1:5]
pred$linear[1:5]
```



Here are the coefficient estimates for the models, using function `coef.blblm` with parallel computing using 4 cores.
```{r}
models %>% map( function(x) coef.blblm(x,para = TRUE, core = 4))
```